Verifying Demonstrations

### 2020-04-22 paper/protest-model.tex
Improves description of protest model

  Furthermore, we say that \(\psh\) is \emph{valid} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).

\end{definition}

%A subset of the proof shares forms a participation proof for a protester.
We denote by \(\pshs\) the set of all proof shares,
and we will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
\begin{multline*}
  \pshs_{\cid_0, \pid_0} = \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = 
  \cid_0 \land \pid = \pid_0\}.
\end{multline*}

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  The \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
  set
  \begin{equation}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh \in \pshs_{\cid, \pid} \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
  \end{equation}
  of all proof shares with the same protester and protest identifiers, and valid for any subprotest $p$ of $\prtst$.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

>>>>

  Furthermore, we say that \(\psh\) is \emph{valid} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).
\end{definition}

%A subset of the proof shares forms a participation proof for a protester.
We let \(\pshs\) denote the set of all proof shares.
Let \(
  \pshs_\prtst = \{ \psh \in \pshs \mid
    \exists \sprtst \in \prtst, \psh \sqsubseteq \sprtst \}
\) be the subset of proof shares related to a protest~\(\prtst\).
We denote by \(=_\pid\) the equivalence relation on \(\pshs\) where \((\cid, t, 
l, \pid, \wid) =_\pid (\cid', t', l', \pid', \wid')\) if \(\pid = \pid'\).
%and we will use the following notation to filter out a subset of \(\pshs\) with 
%specific \(\cid\)s and \(\pid\)s:
%\begin{multline*}
%  \pshs_{\cid_0, \pid_0} = \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = 
%  \cid_0 \land \pid = \pid_0\}.
%\end{multline*}

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  We denote by \(\prfs_\prtst = \pshs_\prtst/=_\pid\) the \emph{set of all 
  proofs of participation for the protest~\(\prtst\)}.
  The \emph{participation proof} of a protester with pseudonym~\(i\) who 
  participates in a protest~\(\prtst\) is the set
  \begin{equation}
    \nonumber
    \prf_{i, \prtst} =
    \left\{ (\cid, t, l, \pid, \wid) \in \pshs_\prtst \mid
      \pid = i\right\},
  \end{equation}
  of all proof shares with the same protester and valid for any subprotest of 
  \(\prtst\).
\end{definition}
